Results

### 2022-07-05 docs/00_participants.Rmd
Prepare ICIS presentation

```{r setup, include=FALSE}
knitr::opts_chunk$set(
	echo = FALSE,
	message = TRUE,
	warning = TRUE, 
	cache.extra = knitr::rand_seed,
	out.width = "80%",
	results = "asis",
	dpi = 300,
	dev.args = list(png = list(type = "cairo"))
)
options(
	knitr.kable.NA = '-',
	knitr.duplicate.label = "allow",
	ggplot2.discrete.fill = ggsci::pal_tron("legacy")(7),
	ggplot2.discrete.colour = ggsci::pal_tron("legacy")(7)
)

@@

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(
	echo = FALSE,
	message = TRUE,
	warning = TRUE, 
	cache.extra = knitr::rand_seed,
	out.width = "80%",
	results = "asis",
	dpi = 300,
	dev.args = list(png = list(type = "cairo"))
)

options(
	knitr.kable.NA = '-',
	knitr.duplicate.label = "allow",
	ggplot2.discrete.fill = pal_d3()(4),
	ggplot2.discrete.colour = pal_d3()(4)
)

@@

# Language profile

```{r participants-lp, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}

participants %>% 
	select(participant, age_group, lp, starts_with("doe_"), test_language) %>% 
	mutate(participant = paste0(participant, "(", age_group, ")")) %>% 
	pivot_longer(
		starts_with("doe_"),
		names_to = "language",
		values_to = "doe"
	) %>% 
	mutate(
		language = str_remove_all(language, "doe_") %>% 
			str_to_sentence(),
	) %>% 
	ggplot() +
	aes(
		x = doe,
		y = reorder(participant, lp),
		fill = language
	) +
	facet_wrap(
		lp~test_language,
		scales = "free_y",
		labeller = label_wrap_gen(multi_line = FALSE)
	) +
	geom_col(
		position = position_fill(),
		size = 0.1,
		colour = "white"
	) +
	geom_vline(
		xintercept = 0.5
	) +
	labs(
		x = "Degree of exposure",
		y = "Participant",
		fill = "Language"
	) +
	scale_x_continuous(
		labels = percent
	) +
	theme(
		axis.text.y = element_blank(),
		panel.grid = element_blank(),
		axis.title.y = element_blank(),
		plot.background = element_rect(fill = "white")

	)

ggsave(here("img", "participants_lp.png"))

### 2022-07-05 docs/01_stimuli.Rmd
Prepare ICIS presentation

animacy %>% 
	filter(role=="Prime") %>% 
	ggplot() +
	aes(
		x = trial_type, 
		y = n, 
		fill = is_animate,
		colour = is_animate
	) + 
	facet_wrap(~test_language, ncol = 4) +
	geom_col(position = position_fill()) +
	geom_hline(
		yintercept = 0.5, 
		size = 1,
		colour = "grey"
	) +
	labs(
		title = "Prime", 
		x = "Trial type", 
		y = "# trials",
		colour = "Animacy", 
		fill = "Animacy"
	) +
	scale_y_continuous(labels = percent) +
	coord_flip() + 
	theme(
		axis.title.x = element_blank()
	) +

	animacy %>% 
	filter(role=="Target") %>% 
	ggplot(aes(trial_type, n, fill = is_animate, colour = is_animate)) +
	facet_wrap(~test_language, ncol = 4) +
	geom_col(position = position_fill()) +
	geom_hline(yintercept = 0.5, size = 1, colour = "grey") +
	labs(title = "Target", x = "Trial type", y = "# trials", colour = "Animacy", fill = "Animacy") +
	scale_y_continuous(labels = percent) +
	coord_flip() +

@@

ggsave(here("img", "stimuli_animacy.png"), width = 15)

>>>>

animacy %>% 
	filter(role=="Prime") %>% 
	ggplot() +
	aes(
		x = trial_type, 
		y = n, 
		fill = is_animate,
		colour = is_animate
	) + 
	facet_wrap(~test_language, ncol = 4) +
	geom_col(position = position_fill()) +
	geom_hline(
		yintercept = 0.5, 
		size = 1,
		colour = "grey"
	) +
	labs(
		title = "Prime", 
		x = "Trial type", 
		y = "# trials",
		colour = "Animacy", 
		fill = "Animacy"
	) +
	scale_fill_d3() +
	scale_colour_d3() +
	scale_y_continuous(labels = percent) +
	coord_flip() + 
	theme(
		axis.title.x = element_blank()
	) +

	animacy %>% 
	filter(role=="Target") %>% 
	ggplot(aes(trial_type, n, fill = is_animate, colour = is_animate)) +
	facet_wrap(~test_language, ncol = 4) +
	geom_col(position = position_fill()) +
	geom_hline(yintercept = 0.5, size = 1, colour = "grey") +
	labs(title = "Target", x = "Trial type", y = "# trials", colour = "Animacy", fill = "Animacy") +
	scale_y_continuous(labels = percent) +
	coord_flip() +
	scale_fill_d3() +
		scale_colour_d3() +

@@

ggsave(here("img", "stimuli_semantic-category.png"), width = 15, dpi = 2000)

### 2022-07-05 docs/05_attrition.Rmd
Prepare ICIS presentation

```{r participants_cdi, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=4, out.width="100%"}
# plot participants
participants %>% 
	left_join(distinct(attrition, participant, valid_participant)) %>%
	left_join(vocabulary) %>% 
	drop_na(valid_participant) %>% 
	mutate(
		valid_status = case_when(
			valid_participant & !is.na(vocab_size_l1) ~ "Valid (+ CDI)",
			valid_participant & is.na(vocab_size_l1) ~ "Valid (no CDI)",
			!valid_participant ~ "Not valid"
		)
	) %>% 
	ggplot() +
	aes(lp, fill = valid_status) +
	facet_grid(~age_group, scales = "free") +
	geom_bar(size = 1) +
	geom_hline(
		yintercept = 24,
		linetype = "dashed",
		colour = "white"
	) +
	scale_colour_brewer(palette = "Set1") +
	labs(x = "Group", y = "Sample size", fill = "Valid?") +
	theme(
		legend.position = "top",
		legend.title = element_blank(),
		panel.grid.major.x = element_blank(),
		panel.grid.minor.y = element_blank(),
		axis.title.x = element_blank(),
		axis.text = element_text(size = 10),
		axis.title.y = element_text(angle = 90)
	) 
```

@@

```{r attrition_familiarity_target_causes, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=4, out.width="100%"}
# plot participants
attrition %>% 
	left_join(distinct(stimuli, test_language, location, list, trial, trial_type, familiarity_target)) %>% 
	drop_na(trial_type, familiarity_target) %>% 
	mutate(familiarity_target = round(familiarity_target, digits = 1)) %>% 
	count(trial_type, age_group, valid_status, trial_type, familiarity_target) %>% 
	ggplot(aes(as.factor(familiarity_target), n, fill = valid_status, colour = valid_status)) +
	facet_grid(trial_type~age_group) +
	geom_col(position = position_fill(), colour = "white") +
	labs(x = "Trial type", y = "Trials", colour = "Validity", fill = "Validity") +
	guides(fill = guide_legend(ncol = 2), colour = guide_legend(ncol = 2))	+
	scale_x_discrete(labels = function(x) paste0(as.numeric(x)*100, "%")) +
	scale_y_continuous(labels = percent) +
	coord_flip() +
	theme(
		legend.position = "top",
		legend.title = element_blank(),
		panel.grid = element_blank(),
		axis.text.x = element_text(size = 10),
		axis.text.y = element_text(size = 8),
		axis.title = element_blank()
	)
```

@@

```{r attrition_animacy_target, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
attrition %>% 
	left_join(distinct(stimuli, test_language, location, list, trial, trial_type, is_animate_target)) %>%
	mutate(is_animate_target = ifelse(is_animate_target, "Animate", "Inanimate")) %>% 
	drop_na(trial_type, is_animate_target) %>% 
	count(trial_type, age_group, valid_status, trial_type, is_animate_target) %>% 
	ggplot(aes(as.factor(is_animate_target), n, fill = valid_status, colour = valid_status)) +
	facet_grid(trial_type~age_group) +
	geom_col(position = position_fill(), colour = "white") +
	labs(x = "Trial type", y = "Trials", colour = "Validity", fill = "Validity") +
	guides(fill = guide_legend(ncol = 2), colour = guide_legend(ncol = 2))	+
	scale_y_continuous(labels = percent) +
	coord_flip() +
	theme(
		legend.position = "top",
		legend.title = element_blank(),
		panel.grid = element_blank(),
		axis.text.x = element_text(size = 10),
		axis.text.y = element_text(size = 8),
		axis.title = element_blank()
	)

@@

```{r attrition_category_target, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
attrition %>% 
	left_join(distinct(stimuli, test_language, location, list, trial, trial_type, category_target)) %>%
	drop_na(trial_type, category_target) %>% 
	count(trial_type, age_group, valid_status, trial_type, category_target) %>% 
	ggplot(aes(fct_rev(category_target), n, fill = valid_status, colour = valid_status)) +
	facet_grid(trial_type~age_group) +
	geom_col(position = position_fill(), colour = "white") +
	labs(x = "Trial type", y = "Trials", colour = "Validity", fill = "Validity") +
	guides(fill = guide_legend(ncol = 2), colour = guide_legend(ncol = 2))	+
	scale_y_continuous(labels = percent) +
	coord_flip() +
	theme(
		legend.position = "top",
		legend.title = element_blank(),
		panel.grid = element_blank(),
		axis.text.x = element_text(size = 10),
		axis.text.y = element_text(size = 8),
		axis.title = element_blank()
	)
```

>>>>

```{r participants_cdi, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=4, out.width="100%"}
# plot participants
participants %>% 
	left_join(distinct(attrition, participant, valid_participant)) %>%
	left_join(vocabulary) %>% 
	drop_na(valid_participant) %>% 
	mutate(
		valid_status = case_when(
			valid_participant & !is.na(vocab_size_l1) ~ "Valid (+ CDI)",
			valid_participant & is.na(vocab_size_l1) ~ "Valid (no CDI)",
			!valid_participant ~ "Not valid"
		)
	) %>% 
	ggplot() +
	aes(lp, fill = valid_status) +
	facet_grid(~age_group, scales = "free") +
	geom_bar(size = 1) +
	geom_hline(
		yintercept = 24,
		linetype = "dashed",
		colour = "white"
	) +
	scale_colour_brewer(palette = "Set1") +
	labs(x = "Group", y = "Sample size", fill = "Valid?") +
	theme(
		legend.position = "top",
		legend.title = element_blank(),
		panel.grid.major.x = element_blank(),
		panel.grid.minor.y = element_blank(),
		axis.title.x = element_blank(),
		axis.text = element_text(size = 10),
		axis.title.y = element_text(angle = 90)
	)

ggsave(here("img", "participant_attrition.png"))
```

@@

```{r attrition_familiarity_target_causes, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=4, out.width="100%"}
# plot participants
attrition %>% 
	left_join(distinct(stimuli, test_language, list, trial, trial_type, familiarity_target)) %>% 
	drop_na(
		trial_type, 
		familiarity_target
	) %>% 
	mutate(familiarity_target = round(familiarity_target, digits = 1)) %>% 
	count(
		trial_type,
		age_group,
		valid_status, 
		trial_type, 
		familiarity_target
	) %>% 
	ggplot() +
	aes(
		as.factor(familiarity_target), 
		n, 
		fill = valid_status,
		colour = valid_status
	) +
	facet_grid(trial_type~age_group) +
	geom_col(
		position = position_fill(),
		colour = "white"
	) +
	labs(
		x = "Trial type",
		y = "Trials",
		colour = "Validity", 
		fill = "Validity"
	) +
	guides(
		fill = guide_legend(ncol = 2), 
		colour = guide_legend(ncol = 2)
	)	+
	scale_x_discrete(
		labels = function(x) paste0(as.numeric(x)*100, "%"),
	) +
	scale_y_continuous(labels = percent) +
	scale_fill_d3() +
	coord_flip() +
	theme(
		legend.position = "top",
		legend.title = element_blank(),
		panel.grid = element_blank(),
		axis.text.x = element_text(size = 10),
		axis.text.y = element_text(size = 8),
		axis.title = element_blank()
	)

ggsave(here("img", "attrition_familiarity.png"))
```

@@

```{r attrition_animacy_target, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
attrition %>% 
	left_join(distinct(stimuli, test_language, list, trial, trial_type, is_animate_target)) %>%
	mutate(is_animate_target = ifelse(is_animate_target, "Animate", "Inanimate")) %>% 
	drop_na(trial_type, is_animate_target) %>% 
	count(trial_type, age_group, valid_status, trial_type, is_animate_target) %>% 
	ggplot(aes(as.factor(is_animate_target), n, fill = valid_status, colour = valid_status)) +
	facet_grid(trial_type~age_group) +
	geom_col(position = position_fill(), colour = "white") +
	labs(x = "Trial type", y = "Trials", colour = "Validity", fill = "Validity") +
	guides(fill = guide_legend(ncol = 2), colour = guide_legend(ncol = 2))	+
	scale_y_continuous(labels = percent) +
	coord_flip() +
	theme(
		legend.position = "top",
		legend.title = element_blank(),
		panel.grid = element_blank(),
		axis.text.x = element_text(size = 10),
		axis.text.y = element_text(size = 8),
		axis.title = element_blank()
	)

@@

```{r attrition_category_target, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
attrition %>% 
	left_join(distinct(stimuli, test_language, list, trial, trial_type, category_target)) %>%
	drop_na(
		trial_type, 
		category_target
	) %>% 
	count(
		trial_type,
		age_group,
		valid_status,
		trial_type, 
		category_target
	) %>% 
	ggplot() +
	aes(
		fct_rev(category_target),
		n, 
		fill = valid_status,
		colour = valid_status
	) +
	facet_wrap(
		trial_type~age_group, 
		labeller = label_wrap_gen(multi_line = FALSE),
		scales = "free_y"
	) +
	geom_col(
		position = position_fill(),
		colour = "white"
	) +
	labs(
		x = "Trial type", 
		y = "Trials",
		colour = "Validity",
		fill = "Validity"
	) +
	guides(
		fill = guide_legend(ncol = 2),
		colour = guide_legend(ncol = 2)
	)	+
	scale_y_continuous(labels = percent) +
	coord_flip() +
	theme(
		legend.position = "top",
		legend.title = element_blank(),
		panel.grid = element_blank(),
		axis.text.x = element_text(size = 10),
		axis.text.y = element_text(size = 8),
		axis.title = element_blank()
	)
```

### 2022-07-05 docs/06_results.Rmd
Prepare ICIS presentation

---
title: "Results (Barcelona)"
output: github_document
always_allow_html: true
date: "`r paste0('Updated: ', format(Sys.Date(), '%d/%m/%Y'))`"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
	echo = FALSE,
	message = TRUE,
	warning = TRUE, 
	cache.extra = knitr::rand_seed,
	out.width = "80%",
	results = "asis",
	dpi = 300,
	dev.args = list(png = list(type = "cairo"))
)
options(
	knitr.kable.NA = '-',
	knitr.duplicate.label = "allow",
	ggplot2.discrete.fill = ggsci::pal_futurama()(7),
	ggplot2.discrete.colour = ggsci::pal_futurama()(7)
)

@@

draws %>%
	filter(str_detect(.variable, "time_bin")) %>% 
	ggplot() +
	aes(
		x = .value, 
		y = .variable_name,
		colour = type
	) +
	facet_wrap(
		~type, 
		scales = "free_x"
	) +
	geom_vline(
		xintercept = 0,
		colour = "black",
		linetype = "dashed"
	) +
	stat_pointinterval(
		point_size = 1.5
	) +
	labs(
		x = "Value", 
		y = "Variable", 
		fill = "CrI", 
		alpha = "CrI",
		title = "Polynomial effects"
	) +
	scale_color_d3() +
	guides(fill = "none", color = "none") +
	scale_x_continuous(labels = ~percent(., accuracy = 0.1)) +
	theme(
		axis.title.y = element_blank(),
		panel.border = element_rect(fill = NA, colour = "grey", size = 0.75),
		panel.grid.major.x = element_line(colour = "grey", linetype = "dotted")
	)

@@

corr_mat <- VarCorr(fit_2, summary = TRUE)$participant$cor 
corr_names <- rownames(VarCorr(fit_2, summary = TRUE)$participant$cor)

@@

	labs(x = "Time bin (100 ms)", y = "Expected posterior mean PTLT", colour = "Trial type",
		 fill = "Trial type", shape = "Trial type", linetype = "Trial type") +
	scale_color_futurama() +
	scale_x_continuous(
		breaks = min(gaze$time_bin_center):max(gaze$time_bin_center), 
		labels = 1:20
	) +
	scale_y_continuous(limits = c(0, 1), labels = percent) + 
	theme_minimal() +
	theme(
		legend.position = "top",
		legend.title = element_blank(),
		axis.text.x = element_text(size = 7),
		panel.grid.major.x = element_blank(),
		panel.grid.minor.x = element_blank(),
		panel.background = element_rect(fill = "white", colour = NA),
		plot.background = element_rect(fill = "white", colour = NA)
	)

@@

@@

m <- epred_draws(
	object = fit_3, 
	newdata = nd, 
	ndraws = NULL,
	re_formula = NA
) %>% 
	mutate(
		.value = logit_to_prob(.epred)
	)

m %>% 
	ggplot() +
	aes(
		x = time_bin_center, 
		y = .value,
		colour = trial_type,
		fill = trial_type,
		linetype = trial_type
	) +
	facet_grid(age_group~lp) +
	geom_hline(yintercept = 0.5, colour = "black") +
	# geom_line(
	# 	aes(group = interaction(trial_type, lp, .draw),
	# 		colour = trial_type),
	# 	alpha = 0.5, size = 0.65
	# ) +
	stat_summary(
		fun.data = mean_qi,
		geom = "ribbon",
		colour = NA,
		alpha = 0.1
	) +
	stat_summary(
		fun = mean,
		geom = "line",
		size = 1
	) +
	labs(
		x = "Time bin (100 ms)", 
		y = "Expected posterior mean PTLT",
		colour = "Trial type",
		fill = "Trial type", 
		shape = "Trial type",
		linetype = "Trial type"
	) +
	scale_color_d3() +
	scale_fill_d3() +
	scale_x_continuous(
		breaks = seq(min(gaze$time_bin_center), max(gaze$time_bin_center), len = 5),
		labels = format(100*(seq(0, 20, 5)), big.mark = ",")
	) +
	scale_y_continuous(
		limits = c(0, 1),
		labels = percent
	) + 
	theme(
		legend.position = "top",
		legend.title = element_blank(),
		panel.grid.major.x = element_blank(),
		panel.grid.minor.x = element_blank(),
		panel.background = element_rect(fill = "white", colour = NA),
		plot.background = element_rect(fill = "white", colour = NA)
	)

ggsave(here("img", "predictions.png"))

@@

m <- emmeans(fit_2, ~trial_type | lp, epred = TRUE)

@@

m_draws %>% 
	ggplot() +
	aes(
		x = .value, 
		y = trial_type, 
		fill = trial_type
	) +
	facet_wrap(~lp) +
	stat_slab(
		aes(
			alpha = stat(
				cut_cdf_qi(
					cdf, 
					.width = c(.95, .8, .5), 
					labels = percent_format()
				)
			)
		),
		position = position_nudge(y = 0.05),
		color = "white"
	) +
	stat_pointinterval(
		color = "black"
	) +
	labs(
		x = "Expected posterior mean PTLT",
		y = "Trial type",
		colour = "Trial type", 
		fill = "Trial type",
		alpha = "CrI"
	) +
	guides(
		color = "none",
		fill = "none"
	) +
	scale_alpha_discrete(
		range = c(0.8, 0.2),
		na.translate = FALSE
	) +
	scale_x_continuous(
		limits = c(0, 1),
		labels = percent
	)  +
	theme(
		axis.title.y = element_blank(),
		legend.position = "right",
		panel.grid.major.y = element_blank(),
		panel.grid.minor.y = element_blank(),
		panel.grid.minor.x = element_blank(),
		panel.background = element_rect(fill = NA, colour = "grey")
	)

>>>>

---
title: "Results"
output: github_document
always_allow_html: true
date: "`r paste0('Updated: ', format(Sys.Date(), '%d/%m/%Y'))`"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
	echo = FALSE,
	message = TRUE,
	warning = TRUE, 
	cache.extra = knitr::rand_seed,
	out.width = "80%",
	results = "asis",
	dpi = 300,
	dev.args = list(png = list(type = "cairo"))
)

options(
	knitr.kable.NA = '-',
	knitr.duplicate.label = "allow",
	ggplot2.discrete.fill = pal_d3()(4),
	ggplot2.discrete.colour = pal_d3()(4)
)

@@

draws %>%
	filter(str_detect(.variable, "time_bin")) %>% 
	mutate(
		.variable_name = factor(
			.variable_name,
			levels = c(
				"Main effect",
				"Group (ML vs. BL)",
				"Trial type (U vs. C+NC)",
				"Trial type (C vs. NC)",
				"Trial type (U vs. C+NC) \u00d7 Group",
				"Trial type (C vs. NC) \u00d7 Group"
			)
		)
	) %>% 
	ggplot() +
	aes(
		x = .value, 
		y = fct_rev(.variable_name),
		colour = type
	) +
	facet_wrap(
		~type, 
		scales = "free_x"
	) +
	geom_vline(
		xintercept = 0,
		colour = "black",
		linetype = "dashed"
	) +
	stat_pointinterval(
		point_size = 1.5
	) +
	labs(
		x = "Value", 
		y = "Variable", 
		fill = "CrI", 
		alpha = "CrI",
		title = "Polynomial effects"
	) +
	scale_color_d3() +
	guides(fill = "none", color = "none") +
	scale_x_continuous(labels = ~percent(., accuracy = 0.1)) +
	theme(
		axis.title.y = element_blank(),
		axis.text.y = element_text(hjust = 1),
		panel.border = element_rect(fill = NA, colour = "grey", size = 0.75),
		panel.grid.major.x = element_line(colour = "grey", linetype = "dotted")
	)

ggsave(here("img", "results_polynomial_terms.png"))
```

@@

corr_mat <- VarCorr(fit_3, summary = TRUE)$participant$cor 
corr_names <- rownames(VarCorr(fit_3, summary = TRUE)$participant$cor)

@@

	labs(x = "Time bin (100 ms)", y = "Expected posterior mean PTLT", colour = "Trial type",
		 fill = "Trial type", shape = "Trial type", linetype = "Trial type") +
	scale_color_futurama() +
	scale_x_continuous(
		breaks = min(gaze$time_bin_center):max(gaze$time_bin_center), 
		labels = 1:20
	) +
	scale_y_continuous(
		limits = c(0, 1), 
		labels = percent
	) + 
	theme_minimal() +
	theme(
		legend.position = "top",
		legend.title = element_blank(),
		axis.text.x = element_text(size = 7),
		panel.grid.major.x = element_blank(),
		panel.grid.minor.x = element_blank(),
		panel.background = element_rect(fill = "white", colour = NA),
		plot.background = element_rect(fill = "white", colour = NA)
	)

@@

observed <- fit_3$data %>% 
	group_by(time_bin_center, trial_type, lp, age_group) %>% 
	summarise(
		.value = logit_to_prob(mean(logit, na.rm = TRUE)),
		n = n(),
		.groups = "drop"
	) %>% 
	mutate(.value_se = sd(.value, na.rm = TRUE) / sqrt(n))

nd <- expand_grid(
	lp = c("Monolingual", "Bilingual"),
	trial_type = unique(gaze$trial_type),
	age_group = unique(gaze$age_group),
	time_bin_center = seq(
		min(gaze$time_bin_center), 
		max(gaze$time_bin_center), 
		0.1
	)
)

m <- epred_draws(
	object = fit_3, 
	newdata = nd, 
	# ndraws = 20,
	re_formula = NA
) %>% 
	mutate(
		.value = logit_to_prob(.epred)
	)

m %>% 
	ggplot() +
	aes(
		x = time_bin_center, 
		y = .value,
		colour = trial_type,
		fill = trial_type,
		linetype = trial_type,
		shape = trial_type
	) +
	facet_wrap(
		fct_rev(lp)~age_group,
		scales = "free",
		labeller = label_wrap_gen(multi_line = FALSE)
	) +
	geom_hline(
		yintercept = 0.5,
		colour = "black"
	) +
	# geom_line(
	# 	aes(group = interaction(trial_type, lp, .draw),
	# 		colour = trial_type),
	# 	alpha = 0.5, size = 0.65
	# ) +
	stat_summary(
		fun.data = mean_qi,
		geom = "ribbon",
		colour = NA,
		alpha = 0.25
	) +
	stat_summary(
		fun = mean,
		geom = "line",
		size = 0.75
	) +
	geom_text(
		data = sample_size,
		aes(
			x = min(gaze$time_bin_center),
			y = 1,
			label = paste0("N = ", n)
		),
		colour = "black",
		hjust = 0,
		vjust = 1,
		inherit.aes = FALSE
	) +
	geom_point(
		data = observed,
		size = 1.5
	) +
	labs(
		x = "Time from target-distractor onset (ms)", 
		y = "Posterior mean PTLT",
		colour = "Trial type",
		fill = "Trial type", 
		shape = "Trial type",
		linetype = "Trial type"
	) +
	scale_color_d3() +
	scale_fill_d3() +
	scale_x_continuous(
		breaks = seq(
			min(gaze$time_bin_center),
			max(gaze$time_bin_center),
			len = 7
		),
		labels = format(
			100*(seq(3, 18, 3)), 
			big.mark = ",", trim = TRUE
		)
	) +
	scale_y_continuous(
		limits = c(0, 1),
		labels = percent
	) + 
	theme_custom() +
	theme(
		legend.position = "top",
		legend.title = element_blank(),
		axis.text.x = element_text(face = "plain"),
		axis.text.y = element_text(face = "plain"),
		panel.grid.major.x = element_blank(),
		panel.grid.minor.x = element_blank(),
		panel.background = element_rect(
			fill = NA, 
			colour = NA
		),
		plot.background = element_rect(
			fill = "white",
			colour = NA
		)
	)

ggsave(
	here("img", "predictions.png"),
	dpi = 2000,
	height = 7,
	width = 12
)

```{r gaze_time_observed, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}

sample_size <- participants %>% 
	filter(valid_participant) %>% 
	count(lp, age_group)

observed <- fit_3$data %>% 
	group_by(time_bin_center, trial_type, lp, age_group) %>% 
	summarise(
		.value = logit_to_prob(mean(logit, na.rm = TRUE)),
		n = n(),
		.groups = "drop"
	) %>% 
	mutate(.value_se = sd(.value, na.rm = TRUE) / sqrt(n))

@@

m <- epred_draws(
	object = fit_3, 
	newdata = nd, 
	# ndraws = 20,
	re_formula = NA
) %>% 
	mutate(
		.value = logit_to_prob(.epred)
	)

m %>% 
	ggplot() +
	aes(
		x = time_bin_center, 
		y = .value,
		colour = trial_type,
		fill = trial_type,
		linetype = trial_type,
		shape = trial_type
	) +
	facet_grid(lp~age_group) +
	geom_hline(
		yintercept = 0.5,
		colour = "black"
	) +
	geom_line(
		data = observed
	) +
	geom_point(
		data = observed,
		size = 3
	) +
	geom_text(
		data = sample_size,
		aes(
			x = min(gaze$time_bin_center),
			y = 1,
			label = paste0("N = ", n)
		),
		colour = "black",
		hjust = 0,
		vjust = 1,
		inherit.aes = FALSE
	) +
	labs(
		x = "Time bin (100 ms)", 
		y = "Expected posterior mean PTLT",
		colour = "Trial type",
		fill = "Trial type", 
		shape = "Trial type",
		linetype = "Trial type"
	) +
	scale_color_d3() +
	scale_fill_d3() +
	scale_x_continuous(
		breaks = seq(
			min(gaze$time_bin_center),
			max(gaze$time_bin_center),
			len = 5
		),
		labels = format(
			100*(seq(0, 20, 5)), 
			big.mark = ","
		)
	) +
	scale_y_continuous(
		limits = c(0, 1),
		labels = percent
	) + 
	theme(
		legend.position = "top",
		legend.title = element_blank(),
		panel.grid.major.x = element_blank(),
		panel.grid.minor.x = element_blank(),
		panel.background = element_rect(fill = "white", colour = NA),
		plot.background = element_rect(fill = "white", colour = NA)
	)

ggsave(here("img", "predictions_observed.png"))

@@

m <- emmeans(fit_3, ~trial_type | age_group, by = "lp", epred = TRUE)

@@

m_draws %>% 
	ggplot() +
	aes(
		x = .value, 
		y = trial_type, 
		fill = trial_type
	) +
	facet_grid(lp~age_group) +
	stat_slab(
		aes(
			alpha = stat(
				cut_cdf_qi(
					cdf, 
					.width = c(.95, .8, .5), 
					labels = percent_format()
				)
			)
		),
		position = position_nudge(y = 0.05),
		color = "white"
	) +
	stat_pointinterval(
		color = "black"
	) +
	labs(
		x = "Expected posterior mean PTLT",
		y = "Trial type",
		colour = "Trial type", 
		fill = "Trial type",
		alpha = "CrI"
	) +
	guides(
		color = "none",
		fill = "none"
	) +
	scale_alpha_discrete(
		range = c(0.8, 0.2),
		na.translate = FALSE
	) +
	scale_x_continuous(
		limits = c(0, 1),
		labels = percent
	)  +
	theme(
		axis.title.y = element_blank(),
		legend.position = "right",
		panel.grid.major.x = element_line(colour = "grey", linetype = "dotted"),
		panel.background = element_rect(fill = NA, colour = "grey")
	)
